Dynamic strategies for yaw and induction control of wind farms based on large-eddy simulation and optimization

### 2018-01-02 MuntersMeyers_DynamicStrategiesControl_revision_WM01.tex
R2C3

As is common practice in PDE-constrained optimization, the problem is solved in a reduced formulation: the dependency of the state variables on the controls, i.e. $\bs{q}(\bs{\varphi})$, is explicitly satisfied by fulfilling the state equations in every step throughout the optimization process, which allows to solve a reduced control-space optimization problem in which the reduced cost functional $\tilde{\J}(\bs{\varphi}) \equiv \J \big(\bs{\varphi},\bs{q}(\bs{\varphi}) \big)$ is minimized, subject only to the box constraints in equations \eqref{eq:boxct_constraint} - \eqref{eq:boxomega_constraint}. The latter problem is solved using the L-BFGS-B algorithm \cite{byrd1995limited}, which is an iterative limited-memory quasi-Newton algorithm that uses gradient information to construct and optimize a quadratic model of the cost functional in each iteration while attempting to satisfy the strong Wolfe conditions \cite{wolfe1969convergence}. As shown in Figure \ref{fig:receding_horizon}, within each optimization window, the iterative procedure hence results in repeated alternating evaluations of the cost functional (i.e. flow simulations using LES) and gradient (i.e. adjoint simulations, see below).

>>>>

As is common practice in PDE-constrained optimization, the problem is solved in a reduced formulation: the dependency of the state variables on the controls, i.e. $\bs{q}(\bs{\varphi})$, is explicitly satisfied by fulfilling the state equations in every step throughout the optimization process, which allows to solve a reduced control-space optimization problem in which the reduced cost functional $\tilde{\J}(\bs{\varphi}) \equiv \J \big(\bs{\varphi},\bs{q}(\bs{\varphi}) \big)$ is minimized, subject only to the box constraints in equations \eqref{eq:boxct_constraint} - \eqref{eq:boxomega_constraint}. The latter problem is solved using the \revision{L-BFGS-B (limited-memory Broyden--Fletcher--Goldfarb--Shanno with bounds support) algorithm \cite{byrd1995limited}}, which is an iterative quasi-Newton algorithm that uses gradient information to construct and optimize a quadratic model of the cost functional in each iteration while attempting to satisfy the strong Wolfe conditions \cite{wolfe1969convergence}. As shown in Figure \ref{fig:receding_horizon}, within each optimization window, the iterative procedure hence results in repeated alternating evaluations of the cost functional (i.e. flow simulations using LES) and gradient (i.e. adjoint simulations, see below).
